\input{preamble.tex}

\colorlet{body}{Black}

\renewcommand{\photo}[2]{}

% Remove Margin Notes only in monochrome mode
\ifmonochrome
  \renewcommand{\marginpar}[1]{}
\fi

\geometry{
  left=2cm,
  right=2cm,
  top=2cm,
  bottom=2cm,
  portrait
}

\setmainfont{NotoSans-Regular}[
  Path = ./fonts/,
  Extension = .ttf
]

\begin{document}

\makecvheader

\vspace{1cm}
\indent\textbf{Hiring Management Team}\\
\indent\textbf{Company Name}

\vspace{0.5cm}

\noindent To whom it may concern:

\vspace{0.5cm}

\justifying

<<<<<<< Updated upstream
\text{I am writing to express my enthusiasm for the Senior Technology Specialist position at Innovative Solutions Inc. With my current studies for my Bachelor of Science in Technological Entrepreneurship and Management, extensive experience in technology support and development, and a mission dedicated to empowering individuals through innovative technology, I bring a unique blend of skills and passion to your team. I am excited about the opportunity to contribute to your mission to drive technological advancement for a more resilient and hopeful world.}\\\\
\text{In my recent role as a Technology Support Specialist at Tolleson Union High School District, I successfully oversaw the deployment of over 3,000 devices across a large high school campus, ensuring seamless integration and functionality for staff and students. This experience honed my skills in end-user support, device management, and network troubleshooting—critical requirements listed in your job posting. Additionally, I developed a Microsoft Power App that integrated Office365 and SharePoint data, reducing user information requests by over 90\% and significantly improving response times. My ability to create efficient solutions aligns with Innovative Solutions Inc.’s commitment to leveraging technology to solve complex problems.}\\\\
\text{The Senior Technology Specialist role at Innovative Solutions Inc. may require advanced machine learning and cybersecurity expertise, where my direct experience is still growing. However, my foundation in Python, Rust, and RESTful API integration, combined with my proven ability to learn and implement new technologies quickly, positions me to acquire and excel in these areas rapidly. My proactive approach to continuous learning and my track record of successfully adapting to new challenges will enable me to bridge any gaps effectively.}\\\\
\text{What excites me most about Innovative Solutions Inc. is your dedication to fostering a collaborative and innovative work environment that prioritizes technological excellence and social impact. Your company’s vision to create solutions that advance business objectives and contribute positively to society resonates deeply with my mission to empower individuals through technology. I am eager to bring my cross-cultural communication skills, project management expertise, and passion for technology to your esteemed team.}\\\\
\text{My technical skills, dedication to continuous improvement, and ability to work collaboratively across departments make me a strong candidate for the Senior Technology Specialist position. I would welcome the opportunity to discuss how my background, skills, and mission align with the goals of Innovative Solutions Inc. Thank you for considering my application. I look forward to contributing to your team and supporting your mission to create a more resilient and hopeful world through technology.}
=======
\text{I am writing to express my enthusiasm for the Software Engineer position at ServiceNow. With my current studies for my Bachelor of Science in Technological Entrepreneurship and Management, extensive experience in software development, and a mission dedicated to empowering individuals through innovative technology, I bring a unique blend of skills and passion to your team. I am excited about the opportunity to contribute to your mission of building AI-enhanced technology solutions that drive scalability and reusability.} \\\\
\text{In my recent role as a Technology Support Specialist at Tolleson Union High School District, I successfully oversaw the deployment of over 3,000 devices across a large high school campus, ensuring seamless integration and functionality for staff and students. Additionally, I developed a Microsoft Power App with Office365 and SharePoint data integrations, reducing user information requests by 90\%. My focus on building scalable, user-friendly solutions aligns well with ServiceNow’s goals.} \\\\
\text{The Software Engineer role at ServiceNow requires expertise in JavaScript and modern UI frameworks like Angular, React, or Vue. In my work as a developer, I’ve built scalable web applications using React and have significant experience in RESTful API integration and front-end development. I am highly adaptable and continuously expanding my skillset in areas such as object-oriented programming, data structures, and algorithms, making me a strong fit for this role.} \\\\
\text{What excites me most about ServiceNow is your commitment to innovation, customer success, and collaboration. Your AI-driven products and cloud-based solutions play a vital role in advancing business processes while making technology more accessible and scalable. I am eager to bring my problem-solving skills, dedication to clean code, and passion for developing user-centered products to your esteemed team.} \\\\
\text{Thank you for considering my application. I look forward to the opportunity to discuss how my background, skills, and mission align with the goals of ServiceNow. I am confident that my passion for software engineering and my focus on continuous improvement will allow me to contribute meaningfully to your team.}
>>>>>>> Stashed changes

\vspace{0.5cm}

\noindent Respectfully, \\
\noindent \textbf{Enoch Lindeman}

\end{document}
