\name{Enoch Lindeman}
\tagline{Network Specialist / Systems Engineer \\Cofounder \& Owner, by The Lindemans, LLC}
\personalinfo{
  \mailaddress{enoch@lindeman.family}
  \phone{(619) 333-8221}\\
  \linkedin{www.linkedin.com/in/enoch-lindeman}
  \location{San Diego, CA}
}

\input{preamble.tex}

\begin{document}

\makecvheader

\cvsection{Summary}
\begin{quote}
  \noindent
  Network Specialist and Systems Engineer with over 6 years of experience in **network design**, **hardware and software integration**, and **systems engineering**. Strong expertise in **IPv6 protocol**, quality assurance, and designing integrated IT solutions for high-performance computing environments. Skilled in analyzing user needs, developing software solutions, and leading system-level testing to ensure optimal network performance and operational efficiency.
\end{quote}

\cvsection{Experience}
\cvevent{Network Specialist / Systems Engineer}{Tolleson Union High School District}{Jun 2022 -- Ongoing}{San Diego, CA}
\par\smallskip
\noindent
\begin{minipage}{20cm}
  \begin{minipage}{9.75cm}
    \text{Led the design, integration, and implementation of network systems}
    \begin{itemize}
      \item Managed integration of **IPv6** and other networking protocols to enhance system performance and meet modern connectivity requirements.
      \item Designed and implemented high-performance computing environments, optimizing hardware and software integration.
    \end{itemize}
  \end{minipage}
  \hfill
  \begin{minipage}{9.75cm}
    \text{Performed system-level testing and quality assurance reviews}
    \begin{itemize}
      \item Conducted comprehensive quality assurance reviews, ensuring the compatibility and performance of new and existing software products.
      \item Developed integrated system test strategies to validate system performance and compliance with operational specifications.
    \end{itemize}
  \end{minipage}
\end{minipage}
\par\smallskip
\divider

\cvevent{Owner \& Network Engineer}{by The Lindemans}{Dec 2022 -- Ongoing}{San Diego, CA}
\par\smallskip
\noindent
\begin{minipage}{20cm}
  \begin{minipage}{9.75cm}
    \text{Provided IT solutions for client networks and high-performance computing environments}
    \begin{itemize}
      \item Led network and systems integration projects for business and industrial clients, focusing on optimizing operational efficiency and scalability.
      \item Designed software solutions for custom applications, enhancing operational capabilities through tailored IT solutions.
    \end{itemize}
  \end{minipage}
  \hfill
  \begin{minipage}{9.75cm}
    \text{Collaborated with stakeholders to implement client-focused IT strategies}
    \begin{itemize}
      \item Analyzed user needs and developed software solutions to optimize business operations and IT performance.
      \item Coordinated with cross-functional teams to deliver integrated hardware and software solutions that aligned with business goals.
    \end{itemize}
  \end{minipage}
\end{minipage}
\par\smallskip
\divider

\cvevent{Mission Technology Specialist}{The Church of Jesus Christ of Latter-Day Saints}{May 2020 -- May 2022}{Syracuse, NY}
\par\smallskip
\noindent
\begin{minipage}{20cm}
  \begin{minipage}{9.75cm}
    \text{Developed software solutions and network systems for distributed applications}
    \begin{itemize}
      \item Led the integration of network protocols, including **IPv6**, into distributed computing systems, improving system reliability and connectivity.
      \item Developed test strategies and performed system-level testing, ensuring smooth operation across the network infrastructure.
    \end{itemize}
  \end{minipage}
  \hfill
  \begin{minipage}{9.75cm}
    \text{Supported the design and implementation of IT solutions}
    \begin{itemize}
      \item Provided technical support for high-performance computing systems and ensured system efficiency through comprehensive testing and diagnostics.
      \item Analyzed and designed database systems, improving operational performance through software customization.
    \end{itemize}
  \end{minipage}
\end{minipage}

\cvsection{Education}
\cvevent{Bachelor of Science in Technological Entrepreneurship and Management}{Arizona State University}{Expected May 2026}{Online}
\begin{itemize}
  \item Current GPA: 4.0
  \item Coursework includes network systems design, high-performance computing, and database integration.
\end{itemize}
\divider

\cvevent{Associate of Science in Computer Science}{Rio Salado College}{August 2024}{Tempe, AZ}
\begin{itemize}
  \item Graduated Summa Cum Laude, GPA: 3.9
  \item Specialized in network engineering, IPv6 integration, and IT solutions for high-performance computing.
\end{itemize}

\cvsection{Skills}
\noindent
\begin{minipage}{20cm}
  \cvtag{IPv6}
  \cvtag{High-Performance Computing}
  \cvtag{Network Design \& Integration}
  \cvtag{Systems Engineering}
  \cvtag{Software Integration}
  \cvtag{Quality Assurance}
  \cvtag{Systems Testing \& Validation}
  \cvtag{Database Design}
  \cvtag{Microsoft Office Suite (Word, Excel, PowerPoint)}
  \cvtag{Cross-functional Team Collaboration}
  \cvtag{Client-Focused IT Solutions}
\end{minipage}

\end{document}